---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# msafer

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN
status](https://www.r-pkg.org/badges/version/msafer)](https://CRAN.R-project.org/package=msafer)
[![Build Status](https://travis-ci.com/kpien/msafer.svg?branch=master)](https://travis-ci.com/kpien/msafer)
<!-- badges: end -->

**msafer** is a package that frees users from having to manually find the location of an error when using the function `map()`. When `map()` returns an error, it's unclear where this error occurs. The function `map_safe()` takes in a vector, function and requirements, and spits out `TRUE` or `FALSE` based on whether an error occurs when running the function over the vector. `map_safe()` will return a list of logical returns where it will be easy to identify the place of the error. 

## Installation

You can install the development version of msafer from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("kpien/msafer")
```
## Example

For demonstration purposes, let's create a sample list of dataframes from the `starwars` and `mtcars` datasets.

```{r, message=FALSE}
library(dplyr)
sample_a <- starwars %>%
  sample_n(34) %>%
  select(-height, -hair_color)
sample_b <- sample_n(starwars, 35)
sample_c <- mtcars %>%
  sample_n(20) %>%
  select(-hp)
sample_d <- tibble::tibble()
list_sample <- list(starwars, sample_a, sample_b, sample_c, mtcars, sample_d)
```

Pass `map_safe_merge()` the same arguments as `map()`. These would be the list of dataframes, the function to map over all the dataframes, and any arguments that the function needs. `map_safe_merge()` will return a tibble with the file numbers and any errors that may have occurred while trying to apply `map()`, grouping repeat errors together.

```{r example}
library(msafer)
map_safe_merge(list_sample, select, height)
```

However, if the vector is huge, then the result would be messy and hard to grab information from the tibble. Thus, we can use `map_safe()` which nests the error message, and returns a tibble that contains only the unique error message and the index locating where the error occurs within the vector.
```{r}
sample_df <- map_safe(list_sample, dplyr::select, height)
sample_df
sample_df %>% 
  tidyr::unnest(which_id)
```

`check_match()` identified whether the user’s requirement existed within the dataset/list of dataframes, if yes, then the function will return `TRUE`, if not, it returns `FALSE`.
```{r}
check_match(dplyr::starwars, height == 172)
```

`check_match()` and also be used under `map_safe()` when applying `check_match()` to a vector which could contain multiple elements  
```{r}
d <- map_safe(list_sample, check_match,  height == 172)
d
```


## Developed By

- [Sifan(Carol) Liu](https://github.com/CarolLiuSifan)
- [Kelly Pien](https://github.com/kpien)
- [Huiqing(Lily) Jin](https://github.com/Lilyyyy54)
