---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# msafer

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN
status](https://www.r-pkg.org/badges/version/msafer)](https://CRAN.R-project.org/package=msafer)
[![Build Status](https://travis-ci.com/kpien/msafer.svg?branch=master)](https://travis-ci.com/kpien/msafer)
<!-- badges: end -->

**msafer** is a package that frees users from having to manually find the location of an error when using the function `map()`. When `map()` returns an error, it's unclear where this error occurs. The function `map_safe()` takes in a vector, function and requirements, and spits out `TRUE` or `FALSE` based on whether an error occurs when running the function over the vector. `map_safe()` will return a list of logical returns where it will be easy to identify the place of the error. 

## Installation

You can install the development version of msafer from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
devtools::install_github("kpien/msafer")
```
## Example

For demonstration purposes, let's create a sample list of dataframes from the `starwars` and `mtcars` datasets.

```{r}
sample_a <- sample_n(starwars, 34)
sample_a <- subset(sample_a, select = -c(height,hair_color))
sample_b <- sample_n(starwars, 35)
sample_c <- sample_n(mtcars, 20)
sample_c <- subset(sample_c, select = -c(hp))
sample_d <- tibble()
list_sample <- list(starwars, sample_a, sample_b, sample_c, mtcars, sample_d)
```

Pass `map_safe_merge()` the same arguments as `map()`. These would be the list of dataframes, the function to map over all the dataframes, and any arguments that the function needs. `map_safe_merge()` will return a tibble with the file numbers and any errors that may have occurred while trying to apply `map()`, grouping repeat errors together.

```{r example}
library(msafer)
map_safe_merge(list_sample, dplyr::select, height)
```

However, if the vector is huge, then the result would be messy and hard to grab information from the tibble. Thus, we can use `map_safe()` which nests the error message, and returns a tibble that contains only the unique error message and the index locating where the error occurs within the vector.
```{r}
sample_df <- map_safe(list_sample, dplyr::select, height)
sample_df
```


## Developed By
Sifan(Carol) Liu, Kelly Pien, Huiqing(Lily) Jin
